---
title: "Versatile Exploration of Data: Coefficient of Variation"
author: "Maani Beigy"
date: "February 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


$$\sum_{i=1}^{n} X^3_i$$
$$
\begin{aligned}
 AR(p): Y_i &= c + \epsilon_i + \phi_i Y_{i-1} \dots \\
 Y_{i} &= c + \phi_i Y_{i-1} \dots
\end{aligned}
$$

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```
cqv <- function(x, na.rm = FALSE, digits = NULL, CI = NULL, R = NULL, ...) {
    if (!is.numeric(x)) {
        stop("argument is not numeric: returning NA")
        return(NA_real_)
    }
    if (!is.vector(x)) {
        stop("x is not a vector")
        return(NA_real_)
    }
    # library(dplyr)
    # library(SciViews)
    # library(boot)
    na.rm = na.rm  # removes NAs if TRUE
    if (is.null(digits)) {
        digits = 4
    }
    digits = digits  # digits required for rounding
    CI = CI  # returns 95% confidence interval if TRUE
    if (is.null(R)) {
        R = 1000
    }
    q3 <- unname(
        quantile(
            x,
            probs = 0.75,  # third quartile (0.75 percentile)
            na.rm = na.rm
        )
    )
    q1 <- unname(
        quantile(
            x,
            probs = 0.25,  # first quartile (0.75 percentile)
            na.rm = na.rm
        )
    )
    if (q3 == 0) {  # to avoid NaNs when q3 and q1 are zero
        q3 <- max(x)
    }
    a <- ceiling(
        (length(x)/4) - (1.96 * (((3 * length(x))/16)^(0.5)))
    )
    b <- round(
        (length(x)/4) + (1.96 * (((3 * length(x))/16)^(0.5))),
        digits = 0
    )
    c <- length(x) + 1 - b
    d <- length(x) + 1 - a
    Ya <- nth(x, a, order_by = x)
    Yb <- nth(x, b, order_by = x)
    Yc <- nth(x, c, order_by = x)
    Yd <- nth(x, d, order_by = x)
    star <- 0
    for (i in a:(b - 1)) {
        star[i] <- (
            (choose(length(x), i)) * (0.25^(i)) * (0.75^(length(x) - i))
        )
        alphastar <- 1 - sum(star[i])
    }
    zzz <- qnorm((1 - ((1 - alphastar)/2)))
    f1square <- (3 * (zzz)^2)/(4 * length(x) * ((Yb - Ya)^2))
    f3square <- (3 * (zzz)^2)/(4 * length(x) * ((Yd - Yc)^2))
    D <- q3 - q1
    S <- q3 + q1
    v <- (
        (1/(16 * length(x))) * (
            (((3/f1square) + (3/f3square) - (2/sqrt(f1square * f3square))) / D^2) +
                (((3/f1square) + (3/f3square) + (2/sqrt(f1square * f3square))) / S^2) -
                ((2 * ((3/f3square) - (3/f1square)))/(D*S))
        )
    )
    ccc <- length(x)/(length(x) - 1)
    upper.tile <- exp(((ln((D/S)) * ccc)) + (zzz * (v^(0.5))))
    lower.tile <- exp(((ln((D/S)) * ccc)) - (zzz * (v^(0.5))))
    boot.cqv <- boot(
        x,
        function(x, i) {
            round(((
                unname(quantile(x[i], probs = 0.75, na.rm = na.rm)) -
                    unname(quantile(x[i], probs = 0.25, na.rm = na.rm))
            ) / (
                unname(quantile(x[i], probs = 0.75, na.rm = na.rm)) +
                    unname(quantile(x[i], probs = 0.25, na.rm = na.rm))
            )) * 100, digits = digits)
        },
        R = R
    )
    if (is.null(CI)) {
        boot.cqv.ci <- NA
    } else if (CI == "Bonett") {
        boot.cqv.ci <- NA
    } else if (CI == "norm") {
        boot.cqv.ci <- boot.ci(boot.cqv, conf = 0.95, type = "norm")
    } else if (CI == "basic") {
        boot.cqv.ci <- boot.ci(boot.cqv, conf = 0.95, type = "basic")
    } else if (CI == "stud") {
        boot.cqv.ci <- boot.ci(boot.cqv, conf = 0.95, type = "stud")
    } else if (CI == "perc") {
        boot.cqv.ci <- boot.ci(boot.cqv, conf = 0.95, type = "perc")
    } else if (CI == "bca") {
        boot.cqv.ci <- boot.ci(boot.cqv, conf = 0.95, type = "bca")
    }

    if (is.null(CI)) {
        cqv <- round(
            100 * ((q3 - q1)/(q3 + q1)), digits = digits
        )
    } else if (CI == "Bonett") {
        cqv <- round(
            100 * ((q3 - q1)/(q3 + q1)), digits = digits
        )
    } else if (CI == "norm") {
        cqv <- round(
            100 * ((q3 - q1)/(q3 + q1)), digits = digits
        )
    } else if (CI == "basic") {
        cqv <- round(
            100 * ((q3 - q1)/(q3 + q1)), digits = digits
        )
    } else if (CI == "perc") {
        cqv <- round(
            100 * ((q3 - q1)/(q3 + q1)), digits = digits
        )
    } else if (CI == "bca") {
        cqv <- (
            boot.cqv.ci$bca[2]
        )
    }

    if (is.null(CI)) {
        CI95 <- NA
    } else if (CI == "Bonett") {
        CI95 <- paste0(
            round(lower.tile * 100, digits = digits),
            "-",
            round(upper.tile * 100, digits = digits)
        )
    } else if (CI == "norm") {
        CI95 <- paste0(
            round(boot.cqv.ci$normal[2], digits = digits),
            "-",
            round(boot.cqv.ci$normal[3], digits = digits)
        )
    } else if (CI == "basic") {
        CI95 <- paste0(
            round(boot.cqv.ci$basic[4], digits = digits),
            "-",
            round(boot.cqv.ci$basic[5], digits = digits)
        )
    } else if (CI == "perc") {
        CI95 <- paste0(
            round(boot.cqv.ci$percent[4], digits = digits),
            "-",
            round(boot.cqv.ci$percent[5], digits = digits)
        )
    } else if (CI == "bca") {
        CI95 <- paste0(
            round(boot.cqv.ci$bca[4], digits = digits),
            "-",
            round(boot.cqv.ci$bca[5], digits = digits)
        )
    }

    if (is.null(CI)) {
        return(
            structure(
                .Data = c(cqv),
                "dim" = c(1, 1),
                "dimnames" = list(c(" "), c("cqv"))
            )
        )
    } else if (CI == "Bonett") {
        return(
            structure(
                .Data = c(cqv, CI95),
                "dim" = c(1, 2),
                "dimnames" = list(c(" "), c("cqv", "Bonett's 95% CI"))
            )
        )
    } else if (CI == "norm") {
        return(
            structure(
                .Data = c(cqv, CI95),
                "dim" = c(1, 2),
                "dimnames" = list(c(" "),
                                  c("cqv", "normal approximation 95% CI"))
            )
        )
    } else if (CI == "basic") {
        return(
            structure(
                .Data = c(cqv, CI95),
                "dim" = c(1, 2),
                "dimnames" = list(c(" "),
                                  c("cqv", "basic bootstrap 95% CI"))
            )
        )
    } else if (CI == "perc") {
        return(
            structure(
                .Data = c(cqv, CI95),
                "dim" = c(1, 2),
                "dimnames" = list(c(" "),
                                  c("cqv", "bootstrap percentile 95% CI"))
            )
        )
    } else if (CI == "bca") {
        return(
            structure(
                .Data = c(cqv, CI95),
                "dim" = c(1, 2),
                "dimnames" = list(
                    c(" "),
                    c("cqv", "adjusted bootstrap percentile (BCa) 95% CI"))
            )
        )
    } else {
        stop("method for confidence interval is not available")
        return(NA_real_)
    }
}

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
