---
title: "Versatile Exploration of Data: Coefficient of Variation"
author: "Maani Beigy"
date: "February 18, 2019"
output: html_document
bibliography: DescObs.bib
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Coefficient of Variation   
Coefficient of variation *($CV$)* is a measure of relative dispersion representing 
the degree of variability relative to the mean [@Albatineh2014]. 
Since cv is unitless, it is useful for comparison of variables with different 
units [@Albatineh2014]. It is also a measure of homogeneity. The *population* coefficient of variation is:    
$$CV = \frac{\sigma}{\mu},$$
where $\sigma$ is the population standard deviation and $\mu$ is the population mean. Almost always, we analyze data from samples but want to generalize it 
as the population's parameter [@Albatineh2014]. Its sample's estimate is given 
as:    
$$cv = \frac{sd}{\bar{X}}$$   
where $sd$ is the sample standard deviation, the square root of the unbiased estimator of population variance, and $\bar{X}$ is the sample mean. The 
corrected *cv* to account for the sample size is:
$$
cv_{korr} = cv * \biggl(1 - \frac{1}{4(n-1)} 
+ \frac{1}{n}cv^2 
+ \frac{1}{2 (n-1)^2} \biggr)
$$
There are various methods for the calculation of **confidence intervals (CI)** 
for *cv*. All of them are fruitful and have particular use cases. Some of them 
are model-based hence their usage depends the assumptions regarding the distribution of data.   

### Kelley's Method        

Let us assume that *cv* follows a noncentral *t* distribution, when the parent  population of the scores is *normally-distributed*, with noncentrality 
($\lambda$) parameter:   
$$
\lambda = \frac{\sqrt{n}}{cv}
$$
with *v* degrees of freedom, where $v = n - 1$. 
Let $1 - \alpha$ be the CI coverage with $\alpha_L + \alpha_U = \alpha$ in which $\alpha_L$ is the the proportion of times that *cv* will be 
less than the lower confidence bound and $\alpha_U$ the proportion of times that
*cv* will be greater than the upper confidence bound in the CI procedure [@Kelley2007]. The lower confidence tile for $\lambda$ is is the noncentrality parameter that results in $t_{(1-\alpha_L,v,\lambda_L)}=\hat{\lambda}$ and the
upper confdence tile for $\lambda$ is is the noncentrality parameter that 
results in $t_{(\alpha_U,v,\lambda_U)}=\hat{\lambda}$, where $t_{(1-\alpha_L,v,\lambda_L)}=\hat{\lambda}$ is the value of noncentral *t* distribution at the $1-\alpha_L$ **quantile** with noncentrality parameter $\lambda_L$ and $t_{(\alpha_U,v,\lambda_U)}=\hat{\lambda}$ is the value of noncentral *t* distribution at the $\alpha_U$ **quantile** with noncentrality parameter $\lambda_U$, respectively [@Kelley2007].   
Afterwards, we transform the tiles of the confidence interval for $\lambda$, by
dividing the tiles by $\sqrt{n}$ and therafter inversing them; the CI limits of 
$cv$ will be obtaned:  
$$
p\left[\biggl(\frac{\lambda_U}{\sqrt{n}}\biggr)^{-1}
\le cv \le \biggl(\frac{\lambda_L}{\sqrt{n}}\biggr)^{-1}\right] = 1-\alpha
$$
where $p$ stands for *probability*. Thanks to package `MBESS` [@Kelley2018] for 
the computation of confidence limits for the noncentrality parameter from a *t* distribution (`conf.limits.nct`), $cv$ will be obtained as:   
```{r echo = TRUE}
x <- c(
    0.2, 0.5, 1.1, 1.4, 1.8, 2.3, 2.5, 2.7, 3.5, 4.4,
    4.6, 5.4, 5.4, 5.7, 5.8, 5.9, 6.0, 6.6, 7.1, 7.9
)
cv(
    x, 
    na.rm = TRUE, 
    digits = 3, 
    method = "kelley", 
    correction = TRUE, 
    alpha = 0.05
)
```


# References   

