---
title: "Versatile Function for Removing Objects"
author: "Maani Beigy"
date: "February 27, 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rm_versatile}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Versatile Function for Removing Objects    
The traditional [rm](
https://www.rdocumentation.org/packages/base/versions/3.5.2/topics/remove) 
function from `base` package is not a versatile function because it 
cannot handle exceptional objects or string patterns to skip  or remove. 
Moreover, *rm* gives no warning before removing the objects and is not 
interactive. Also, the `pattern` argument of [ls()](
https://www.rdocumentation.org/packages/base/versions/3.5.2/topics/ls) function cannot handle multiple patterns or multiple [regular expressions](
https://www.rdocumentation.org/packages/base/versions/3.5.2/topics/regex).     

This function has been developed for sake of versatility, where you can 
determine exceptional objects and patterns for saving and/or removing objects. 
Also, you receive proper message regarding the final approval of removing 
objects. The search strategy of `rm_versatile` is based upon [apropos](
https://www.rdocumentation.org/packages/utils/versions/3.5.2/topics/apropos) function, which enables you to determine the type or storage mode of the objects (*e.g.,* double, integer, character, *etc.*).   
   
### Examples    
Let us experience such versatility by examples. First we need to make some 
objects in the environment:
```{r echo=FALSE, warning=FALSE, message=FALSE, include = FALSE}
rm_versatile <- function(
    save.objects = NULL,
    save.patterns = NULL,
    rm.objects = NULL,
    rm.patterns = NULL,
    modes = list("integer", "double", "character", "list"),
    envir = .GlobalEnv,
    inherits = FALSE,
    ...
) {
    if (is.null(save.objects)) {
        save.objects = NULL
    } else {
        save.objects = unlist(save.objects)
    }
    if (is.null(save.patterns)) {
        save.patterns = NULL
    } else {
        save.patterns = unlist(save.patterns)
    }
    if (is.null(rm.objects)) {
        rm.objects = NULL
    } else {
        rm.objects = unlist(rm.objects)
    }
    if (is.null(rm.patterns)) {
        rm.patterns = NULL
    } else {
        rm.patterns = unlist(rm.patterns)
    }
    mode <- match.arg(  # match the user's input with available methods
        arg = unlist(modes),
        choices = c(
            "logical", "integer", "double", "complex", "raw", "character",
            "list", "expression", "name", "symbol", "function"
        ),
        several.ok = TRUE
    )
    envir = envir
    inherits = inherits
    if (
        (is.null(save.patterns)) &&
        (is.null(save.objects)) &&
        (is.null(rm.objects)) &&
        (is.null(rm.patterns))
    ) {
        stop("You have selected neither save nor remove objects/patterns!")
    } else if ((!is.null(save.patterns)) ||
               (!is.null(save.objects))
    ) {
        if ("integer" %in% mode) {
            save.mode.integer <- unlist(lapply(
                save.patterns, apropos, mode = "integer")
            )
        } else if (!("integer" %in% mode)) {
            save.mode.integer <- NULL
        }
        if ("double" %in% mode) {
            save.mode.double <- unlist(lapply(
                save.patterns, apropos, mode = "double")
            )
        } else if (!("double" %in% mode)) {
            save.mode.double <- NULL
        }
        if ("character" %in% mode) {
            save.mode.character <- unlist(
                lapply(save.patterns, apropos, mode = "character")
            )
        } else if (!("character" %in% mode)) {
            save.mode.character <- NULL
        }
        if ("list" %in% mode) {
            save.mode.list <- unlist(
                lapply(save.patterns, apropos, mode = "list")
            )
        } else if (!("list" %in% mode)) {
            save.mode.list <- NULL
        }
        if ("logical" %in% mode) {
            save.mode.logical <- unlist(lapply(
                save.patterns, apropos, mode = "logical")
            )
        } else if (!("logical" %in% mode)) {
            save.mode.logical <- NULL
        }
        if ("complex" %in% mode) {
            save.mode.complex <- unlist(lapply(
                save.patterns, apropos, mode = "complex")
            )
        } else if (!("complex" %in% mode)) {
            save.mode.complex <- NULL
        }
        if ("raw" %in% mode) {
            save.mode.raw <- unlist(
                lapply(save.patterns, apropos, mode = "raw")
            )
        } else if (!("raw" %in% mode)) {
            save.mode.raw <- NULL
        }
        if ("expression" %in% mode) {
            save.mode.expression <- unlist(
                lapply(save.patterns, apropos, mode = "expression")
            )
        } else if (!("expression" %in% mode)) {
            save.mode.expression <- NULL
        }
        if ("name" %in% mode) {
            save.mode.name <- unlist(
                lapply(save.patterns, apropos, mode = "name")
            )
        } else if (!("name" %in% mode)) {
            save.mode.name <- NULL
        }
        if ("symbol" %in% mode) {
            save.mode.symbol <- unlist(
                lapply(save.patterns, apropos, mode = "symbol")
            )
        } else if (!("symbol" %in% mode)) {
            save.mode.symbol <- NULL
        }
        if ("function" %in% mode) {
            save.mode.function <- unlist(lapply(
                save.patterns, apropos, mode = "function")
            )
        } else if (!("function" %in% mode)) {
            save.mode.function <- NULL
        }
        save.formula = union(
            c(save.objects),
            c(save.mode.logical, save.mode.integer, save.mode.double,
              save.mode.complex, save.mode.raw, save.mode.character,
              save.mode.list, save.mode.expression, save.mode.name,
              save.mode.symbol, save.mode.function)
        )
        print(setdiff(ls(envir = .GlobalEnv), save.formula))
        ANSWER <- readline(
            "Are you a sure you want to remove these objects? [yes/no]"
        )
        if (substr(ANSWER, 1, 1) == "n") {
            cat("OK, change your patterns and exceptional objects")
        } else {
            rm(
                list = setdiff(ls(envir = .GlobalEnv), save.formula),
                envir = .GlobalEnv,
                inherits = inherits
            )
            message("Done!")
        }
    } else if (
        ((!is.null(rm.objects)) ||
        (!is.null(rm.patterns)))
    ) {
        if ("integer" %in% mode) {
            rm.mode.integer <- unlist(lapply(
                rm.patterns, apropos, mode = "integer")
            )
        } else if (!("integer" %in% mode)) {
            rm.mode.integer <- NULL
        }
        if ("double" %in% mode) {
            rm.mode.double <- unlist(lapply(
                rm.patterns, apropos, mode = "double")
            )
        } else if (!("double" %in% mode)) {
            rm.mode.double <- NULL
        }
        if ("character" %in% mode) {
            rm.mode.character <- unlist(
                lapply(rm.patterns, apropos, mode = "character")
            )
        } else if (!("character" %in% mode)) {
            rm.mode.character <- NULL
        }
        if ("list" %in% mode) {
            rm.mode.list <- unlist(
                lapply(rm.patterns, apropos, mode = "list")
            )
        } else if (!("list" %in% mode)) {
            rm.mode.list <- NULL
        }
        if ("logical" %in% mode) {
            rm.mode.logical <- unlist(lapply(
                rm.patterns, apropos, mode = "logical")
            )
        } else if (!("logical" %in% mode)) {
            rm.mode.logical <- NULL
        }
        if ("complex" %in% mode) {
            rm.mode.complex <- unlist(lapply(
                rm.patterns, apropos, mode = "complex")
            )
        } else if (!("complex" %in% mode)) {
            rm.mode.complex <- NULL
        }
        if ("raw" %in% mode) {
            rm.mode.raw <- unlist(
                lapply(rm.patterns, apropos, mode = "raw")
            )
        } else if (!("raw" %in% mode)) {
            rm.mode.raw <- NULL
        }
        if ("expression" %in% mode) {
            rm.mode.expression <- unlist(
                lapply(rm.patterns, apropos, mode = "expression")
            )
        } else if (!("expression" %in% mode)) {
            rm.mode.expression <- NULL
        }
        if ("name" %in% mode) {
            rm.mode.name <- unlist(
                lapply(rm.patterns, apropos, mode = "name")
            )
        } else if (!("name" %in% mode)) {
            rm.mode.name <- NULL
        }
        if ("symbol" %in% mode) {
            rm.mode.symbol <- unlist(
                lapply(rm.patterns, apropos, mode = "symbol")
            )
        } else if (!("symbol" %in% mode)) {
            rm.mode.symbol <- NULL
        }
        if ("function" %in% mode) {
            rm.mode.function <- unlist(lapply(
                rm.patterns, apropos, mode = "function")
            )
        } else if (!("function" %in% mode)) {
            rm.mode.function <- NULL
        }
        rm.formula = union(
            c(rm.objects),
            c(rm.mode.logical, rm.mode.integer, rm.mode.double,
              rm.mode.complex, rm.mode.raw, rm.mode.character,
              rm.mode.list, rm.mode.expression, rm.mode.name,
              rm.mode.symbol, rm.mode.function)
        )
        print(rm.formula)
        ANSWER <- readline(
            "Are you a sure you want to remove these objects? [yes/no]"
        )
        if (substr(ANSWER, 1, 1) == "n") {
            cat("OK, change your patterns and remove objects")
        } else {
            rm(
                list = rm.formula,
                envir = .GlobalEnv,
                inherits = inherits
            )
            message("Done!")
        }
    } else if (
        ((!is.null(save.patterns)) ||
         (!is.null(save.objects))) &&
        ((!is.null(rm.objects)) ||
         (!is.null(rm.patterns)))
    ) {
        if ("integer" %in% mode) {
            save.mode.integer <- unlist(lapply(
                save.patterns, apropos, mode = "integer")
            )
        } else if (!("integer" %in% mode)) {
            save.mode.integer <- NULL
        }
        if ("double" %in% mode) {
            save.mode.double <- unlist(lapply(
                save.patterns, apropos, mode = "double")
            )
        } else if (!("double" %in% mode)) {
            save.mode.double <- NULL
        }
        if ("character" %in% mode) {
            save.mode.character <- unlist(
                lapply(save.patterns, apropos, mode = "character")
            )
        } else if (!("character" %in% mode)) {
            save.mode.character <- NULL
        }
        if ("list" %in% mode) {
            save.mode.list <- unlist(
                lapply(save.patterns, apropos, mode = "list")
            )
        } else if (!("list" %in% mode)) {
            save.mode.list <- NULL
        }
        if ("logical" %in% mode) {
            save.mode.logical <- unlist(lapply(
                save.patterns, apropos, mode = "logical")
            )
        } else if (!("logical" %in% mode)) {
            save.mode.logical <- NULL
        }
        if ("complex" %in% mode) {
            save.mode.complex <- unlist(lapply(
                save.patterns, apropos, mode = "complex")
            )
        } else if (!("complex" %in% mode)) {
            save.mode.complex <- NULL
        }
        if ("raw" %in% mode) {
            save.mode.raw <- unlist(
                lapply(save.patterns, apropos, mode = "raw")
            )
        } else if (!("raw" %in% mode)) {
            save.mode.raw <- NULL
        }
        if ("expression" %in% mode) {
            save.mode.expression <- unlist(
                lapply(save.patterns, apropos, mode = "expression")
            )
        } else if (!("expression" %in% mode)) {
            save.mode.expression <- NULL
        }
        if ("name" %in% mode) {
            save.mode.name <- unlist(
                lapply(save.patterns, apropos, mode = "name")
            )
        } else if (!("name" %in% mode)) {
            save.mode.name <- NULL
        }
        if ("symbol" %in% mode) {
            save.mode.symbol <- unlist(
                lapply(save.patterns, apropos, mode = "symbol")
            )
        } else if (!("symbol" %in% mode)) {
            save.mode.symbol <- NULL
        }
        if ("function" %in% mode) {
            save.mode.function <- unlist(lapply(
                save.patterns, apropos, mode = "function")
            )
        } else if (!("function" %in% mode)) {
            save.mode.function <- NULL
        }
        save.formula = union(
            c(save.objects),
            c(save.mode.logical, save.mode.integer, save.mode.double,
              save.mode.complex, save.mode.raw, save.mode.character,
              save.mode.list, save.mode.expression, save.mode.name,
              save.mode.symbol, save.mode.function)
        )
        if ("integer" %in% mode) {
            rm.mode.integer <- unlist(lapply(
                rm.patterns, apropos, mode = "integer")
            )
        } else if (!("integer" %in% mode)) {
            rm.mode.integer <- NULL
        }
        if ("double" %in% mode) {
            rm.mode.double <- unlist(lapply(
                rm.patterns, apropos, mode = "double")
            )
        } else if (!("double" %in% mode)) {
            rm.mode.double <- NULL
        }
        if ("character" %in% mode) {
            rm.mode.character <- unlist(
                lapply(rm.patterns, apropos, mode = "character")
            )
        } else if (!("character" %in% mode)) {
            rm.mode.character <- NULL
        }
        if ("list" %in% mode) {
            rm.mode.list <- unlist(
                lapply(rm.patterns, apropos, mode = "list")
            )
        } else if (!("list" %in% mode)) {
            rm.mode.list <- NULL
        }
        if ("logical" %in% mode) {
            rm.mode.logical <- unlist(lapply(
                rm.patterns, apropos, mode = "logical")
            )
        } else if (!("logical" %in% mode)) {
            rm.mode.logical <- NULL
        }
        if ("complex" %in% mode) {
            rm.mode.complex <- unlist(lapply(
                rm.patterns, apropos, mode = "complex")
            )
        } else if (!("complex" %in% mode)) {
            rm.mode.complex <- NULL
        }
        if ("raw" %in% mode) {
            rm.mode.raw <- unlist(
                lapply(rm.patterns, apropos, mode = "raw")
            )
        } else if (!("raw" %in% mode)) {
            rm.mode.raw <- NULL
        }
        if ("expression" %in% mode) {
            rm.mode.expression <- unlist(
                lapply(rm.patterns, apropos, mode = "expression")
            )
        } else if (!("expression" %in% mode)) {
            rm.mode.expression <- NULL
        }
        if ("name" %in% mode) {
            rm.mode.name <- unlist(
                lapply(rm.patterns, apropos, mode = "name")
            )
        } else if (!("name" %in% mode)) {
            rm.mode.name <- NULL
        }
        if ("symbol" %in% mode) {
            rm.mode.symbol <- unlist(
                lapply(rm.patterns, apropos, mode = "symbol")
            )
        } else if (!("symbol" %in% mode)) {
            rm.mode.symbol <- NULL
        }
        if ("function" %in% mode) {
            rm.mode.function <- unlist(lapply(
                rm.patterns, apropos, mode = "function")
            )
        } else if (!("function" %in% mode)) {
            rm.mode.function <- NULL
        }
        rm.formula = union(
            c(rm.objects),
            c(rm.mode.logical, rm.mode.integer, rm.mode.double,
              rm.mode.complex, rm.mode.raw, rm.mode.character,
              rm.mode.list, rm.mode.expression, rm.mode.name,
              rm.mode.symbol, rm.mode.function)
        )
        print(union(setdiff(ls(envir = .GlobalEnv), save.formula), rm.formula))
        ANSWER <- readline(
            "Are you a sure you want to remove these objects? [yes/no]"
        )
        if (substr(ANSWER, 1, 1) == "n") {
            cat("OK, change your patterns and objects")
        } else {
            rm(
                list = union(
                    setdiff(ls(envir = .GlobalEnv), save.formula),
                    rm.formula
                ),
                envir = .GlobalEnv,
                inherits = inherits
            )
            message("Done!")
        }
    }
}
```
```{r eval = TRUE, warning=FALSE, message=FALSE}
a <- 1
b <- "female"
c <- FALSE
d <- 4:10
e <- 5
f <- 6
g <- 7
df1 <- 8
df2 <- 9
dfcol <- 10
dff1 <- 11
dfff3 <- 12
mydata1 <- 13
mymydata <- 14
dataframe1 <- data.frame(
    gender = c("F", "M", "M", "F"),
    score = c(10, 12, 14, 18)
    )
matrix.a <- matrix(1:10, nrow = 2, ncol = 5)
matrix2 <- matrix(1:100, ncol = 2)
x <- c("a", "b", "c", "d")
y <- c("d", "e", "f")
```
Suppose that we want to remove *all* objects **except** for "a", "b", and "c" 
objects and those with "df" and "data" string patterns. 
```{r eval = TRUE, warning=TRUE, message=TRUE}
rm_versatile(
    save.objects = list("a", "b", "c"),
    save.patterns = list("df", "data")
)
```
Let us check what have we done:
```{r eval = TRUE, warning=TRUE, message=TRUE}
ls()
```
Now, imagine that we want to **remove** objects "x" and "y" and those with 
"matrix" pattern. 
```{r echo=FALSE, warning=FALSE, message=FALSE, include = FALSE}
rm_versatile <- function(
    save.objects = NULL,
    save.patterns = NULL,
    rm.objects = NULL,
    rm.patterns = NULL,
    modes = list("integer", "double", "character", "list"),
    envir = .GlobalEnv,
    inherits = FALSE,
    ...
) {
    if (is.null(save.objects)) {
        save.objects = NULL
    } else {
        save.objects = unlist(save.objects)
    }
    if (is.null(save.patterns)) {
        save.patterns = NULL
    } else {
        save.patterns = unlist(save.patterns)
    }
    if (is.null(rm.objects)) {
        rm.objects = NULL
    } else {
        rm.objects = unlist(rm.objects)
    }
    if (is.null(rm.patterns)) {
        rm.patterns = NULL
    } else {
        rm.patterns = unlist(rm.patterns)
    }
    mode <- match.arg(  # match the user's input with available methods
        arg = unlist(modes),
        choices = c(
            "logical", "integer", "double", "complex", "raw", "character",
            "list", "expression", "name", "symbol", "function"
        ),
        several.ok = TRUE
    )
    envir = envir
    inherits = inherits
    if (
        (is.null(save.patterns)) &&
        (is.null(save.objects)) &&
        (is.null(rm.objects)) &&
        (is.null(rm.patterns))
    ) {
        stop("You have selected neither save nor remove objects/patterns!")
    } else if ((!is.null(save.patterns)) ||
               (!is.null(save.objects))
    ) {
        if ("integer" %in% mode) {
            save.mode.integer <- unlist(lapply(
                save.patterns, apropos, mode = "integer")
            )
        } else if (!("integer" %in% mode)) {
            save.mode.integer <- NULL
        }
        if ("double" %in% mode) {
            save.mode.double <- unlist(lapply(
                save.patterns, apropos, mode = "double")
            )
        } else if (!("double" %in% mode)) {
            save.mode.double <- NULL
        }
        if ("character" %in% mode) {
            save.mode.character <- unlist(
                lapply(save.patterns, apropos, mode = "character")
            )
        } else if (!("character" %in% mode)) {
            save.mode.character <- NULL
        }
        if ("list" %in% mode) {
            save.mode.list <- unlist(
                lapply(save.patterns, apropos, mode = "list")
            )
        } else if (!("list" %in% mode)) {
            save.mode.list <- NULL
        }
        if ("logical" %in% mode) {
            save.mode.logical <- unlist(lapply(
                save.patterns, apropos, mode = "logical")
            )
        } else if (!("logical" %in% mode)) {
            save.mode.logical <- NULL
        }
        if ("complex" %in% mode) {
            save.mode.complex <- unlist(lapply(
                save.patterns, apropos, mode = "complex")
            )
        } else if (!("complex" %in% mode)) {
            save.mode.complex <- NULL
        }
        if ("raw" %in% mode) {
            save.mode.raw <- unlist(
                lapply(save.patterns, apropos, mode = "raw")
            )
        } else if (!("raw" %in% mode)) {
            save.mode.raw <- NULL
        }
        if ("expression" %in% mode) {
            save.mode.expression <- unlist(
                lapply(save.patterns, apropos, mode = "expression")
            )
        } else if (!("expression" %in% mode)) {
            save.mode.expression <- NULL
        }
        if ("name" %in% mode) {
            save.mode.name <- unlist(
                lapply(save.patterns, apropos, mode = "name")
            )
        } else if (!("name" %in% mode)) {
            save.mode.name <- NULL
        }
        if ("symbol" %in% mode) {
            save.mode.symbol <- unlist(
                lapply(save.patterns, apropos, mode = "symbol")
            )
        } else if (!("symbol" %in% mode)) {
            save.mode.symbol <- NULL
        }
        if ("function" %in% mode) {
            save.mode.function <- unlist(lapply(
                save.patterns, apropos, mode = "function")
            )
        } else if (!("function" %in% mode)) {
            save.mode.function <- NULL
        }
        save.formula = union(
            c(save.objects),
            c(save.mode.logical, save.mode.integer, save.mode.double,
              save.mode.complex, save.mode.raw, save.mode.character,
              save.mode.list, save.mode.expression, save.mode.name,
              save.mode.symbol, save.mode.function)
        )
        print(setdiff(ls(envir = .GlobalEnv), save.formula))
        ANSWER <- readline(
            "Are you a sure you want to remove these objects? [yes/no]"
        )
        if (substr(ANSWER, 1, 1) == "n") {
            cat("OK, change your patterns and exceptional objects")
        } else {
            rm(
                list = setdiff(ls(envir = .GlobalEnv), save.formula),
                envir = .GlobalEnv,
                inherits = inherits
            )
            message("Done!")
        }
    } else if (
        ((!is.null(rm.objects)) ||
        (!is.null(rm.patterns)))
    ) {
        if ("integer" %in% mode) {
            rm.mode.integer <- unlist(lapply(
                rm.patterns, apropos, mode = "integer")
            )
        } else if (!("integer" %in% mode)) {
            rm.mode.integer <- NULL
        }
        if ("double" %in% mode) {
            rm.mode.double <- unlist(lapply(
                rm.patterns, apropos, mode = "double")
            )
        } else if (!("double" %in% mode)) {
            rm.mode.double <- NULL
        }
        if ("character" %in% mode) {
            rm.mode.character <- unlist(
                lapply(rm.patterns, apropos, mode = "character")
            )
        } else if (!("character" %in% mode)) {
            rm.mode.character <- NULL
        }
        if ("list" %in% mode) {
            rm.mode.list <- unlist(
                lapply(rm.patterns, apropos, mode = "list")
            )
        } else if (!("list" %in% mode)) {
            rm.mode.list <- NULL
        }
        if ("logical" %in% mode) {
            rm.mode.logical <- unlist(lapply(
                rm.patterns, apropos, mode = "logical")
            )
        } else if (!("logical" %in% mode)) {
            rm.mode.logical <- NULL
        }
        if ("complex" %in% mode) {
            rm.mode.complex <- unlist(lapply(
                rm.patterns, apropos, mode = "complex")
            )
        } else if (!("complex" %in% mode)) {
            rm.mode.complex <- NULL
        }
        if ("raw" %in% mode) {
            rm.mode.raw <- unlist(
                lapply(rm.patterns, apropos, mode = "raw")
            )
        } else if (!("raw" %in% mode)) {
            rm.mode.raw <- NULL
        }
        if ("expression" %in% mode) {
            rm.mode.expression <- unlist(
                lapply(rm.patterns, apropos, mode = "expression")
            )
        } else if (!("expression" %in% mode)) {
            rm.mode.expression <- NULL
        }
        if ("name" %in% mode) {
            rm.mode.name <- unlist(
                lapply(rm.patterns, apropos, mode = "name")
            )
        } else if (!("name" %in% mode)) {
            rm.mode.name <- NULL
        }
        if ("symbol" %in% mode) {
            rm.mode.symbol <- unlist(
                lapply(rm.patterns, apropos, mode = "symbol")
            )
        } else if (!("symbol" %in% mode)) {
            rm.mode.symbol <- NULL
        }
        if ("function" %in% mode) {
            rm.mode.function <- unlist(lapply(
                rm.patterns, apropos, mode = "function")
            )
        } else if (!("function" %in% mode)) {
            rm.mode.function <- NULL
        }
        rm.formula = union(
            c(rm.objects),
            c(rm.mode.logical, rm.mode.integer, rm.mode.double,
              rm.mode.complex, rm.mode.raw, rm.mode.character,
              rm.mode.list, rm.mode.expression, rm.mode.name,
              rm.mode.symbol, rm.mode.function)
        )
        print(rm.formula)
        ANSWER <- readline(
            "Are you a sure you want to remove these objects? [yes/no]"
        )
        if (substr(ANSWER, 1, 1) == "n") {
            cat("OK, change your patterns and remove objects")
        } else {
            rm(
                list = rm.formula,
                envir = .GlobalEnv,
                inherits = inherits
            )
            message("Done!")
        }
    } else if (
        ((!is.null(save.patterns)) ||
         (!is.null(save.objects))) &&
        ((!is.null(rm.objects)) ||
         (!is.null(rm.patterns)))
    ) {
        if ("integer" %in% mode) {
            save.mode.integer <- unlist(lapply(
                save.patterns, apropos, mode = "integer")
            )
        } else if (!("integer" %in% mode)) {
            save.mode.integer <- NULL
        }
        if ("double" %in% mode) {
            save.mode.double <- unlist(lapply(
                save.patterns, apropos, mode = "double")
            )
        } else if (!("double" %in% mode)) {
            save.mode.double <- NULL
        }
        if ("character" %in% mode) {
            save.mode.character <- unlist(
                lapply(save.patterns, apropos, mode = "character")
            )
        } else if (!("character" %in% mode)) {
            save.mode.character <- NULL
        }
        if ("list" %in% mode) {
            save.mode.list <- unlist(
                lapply(save.patterns, apropos, mode = "list")
            )
        } else if (!("list" %in% mode)) {
            save.mode.list <- NULL
        }
        if ("logical" %in% mode) {
            save.mode.logical <- unlist(lapply(
                save.patterns, apropos, mode = "logical")
            )
        } else if (!("logical" %in% mode)) {
            save.mode.logical <- NULL
        }
        if ("complex" %in% mode) {
            save.mode.complex <- unlist(lapply(
                save.patterns, apropos, mode = "complex")
            )
        } else if (!("complex" %in% mode)) {
            save.mode.complex <- NULL
        }
        if ("raw" %in% mode) {
            save.mode.raw <- unlist(
                lapply(save.patterns, apropos, mode = "raw")
            )
        } else if (!("raw" %in% mode)) {
            save.mode.raw <- NULL
        }
        if ("expression" %in% mode) {
            save.mode.expression <- unlist(
                lapply(save.patterns, apropos, mode = "expression")
            )
        } else if (!("expression" %in% mode)) {
            save.mode.expression <- NULL
        }
        if ("name" %in% mode) {
            save.mode.name <- unlist(
                lapply(save.patterns, apropos, mode = "name")
            )
        } else if (!("name" %in% mode)) {
            save.mode.name <- NULL
        }
        if ("symbol" %in% mode) {
            save.mode.symbol <- unlist(
                lapply(save.patterns, apropos, mode = "symbol")
            )
        } else if (!("symbol" %in% mode)) {
            save.mode.symbol <- NULL
        }
        if ("function" %in% mode) {
            save.mode.function <- unlist(lapply(
                save.patterns, apropos, mode = "function")
            )
        } else if (!("function" %in% mode)) {
            save.mode.function <- NULL
        }
        save.formula = union(
            c(save.objects),
            c(save.mode.logical, save.mode.integer, save.mode.double,
              save.mode.complex, save.mode.raw, save.mode.character,
              save.mode.list, save.mode.expression, save.mode.name,
              save.mode.symbol, save.mode.function)
        )
        if ("integer" %in% mode) {
            rm.mode.integer <- unlist(lapply(
                rm.patterns, apropos, mode = "integer")
            )
        } else if (!("integer" %in% mode)) {
            rm.mode.integer <- NULL
        }
        if ("double" %in% mode) {
            rm.mode.double <- unlist(lapply(
                rm.patterns, apropos, mode = "double")
            )
        } else if (!("double" %in% mode)) {
            rm.mode.double <- NULL
        }
        if ("character" %in% mode) {
            rm.mode.character <- unlist(
                lapply(rm.patterns, apropos, mode = "character")
            )
        } else if (!("character" %in% mode)) {
            rm.mode.character <- NULL
        }
        if ("list" %in% mode) {
            rm.mode.list <- unlist(
                lapply(rm.patterns, apropos, mode = "list")
            )
        } else if (!("list" %in% mode)) {
            rm.mode.list <- NULL
        }
        if ("logical" %in% mode) {
            rm.mode.logical <- unlist(lapply(
                rm.patterns, apropos, mode = "logical")
            )
        } else if (!("logical" %in% mode)) {
            rm.mode.logical <- NULL
        }
        if ("complex" %in% mode) {
            rm.mode.complex <- unlist(lapply(
                rm.patterns, apropos, mode = "complex")
            )
        } else if (!("complex" %in% mode)) {
            rm.mode.complex <- NULL
        }
        if ("raw" %in% mode) {
            rm.mode.raw <- unlist(
                lapply(rm.patterns, apropos, mode = "raw")
            )
        } else if (!("raw" %in% mode)) {
            rm.mode.raw <- NULL
        }
        if ("expression" %in% mode) {
            rm.mode.expression <- unlist(
                lapply(rm.patterns, apropos, mode = "expression")
            )
        } else if (!("expression" %in% mode)) {
            rm.mode.expression <- NULL
        }
        if ("name" %in% mode) {
            rm.mode.name <- unlist(
                lapply(rm.patterns, apropos, mode = "name")
            )
        } else if (!("name" %in% mode)) {
            rm.mode.name <- NULL
        }
        if ("symbol" %in% mode) {
            rm.mode.symbol <- unlist(
                lapply(rm.patterns, apropos, mode = "symbol")
            )
        } else if (!("symbol" %in% mode)) {
            rm.mode.symbol <- NULL
        }
        if ("function" %in% mode) {
            rm.mode.function <- unlist(lapply(
                rm.patterns, apropos, mode = "function")
            )
        } else if (!("function" %in% mode)) {
            rm.mode.function <- NULL
        }
        rm.formula = union(
            c(rm.objects),
            c(rm.mode.logical, rm.mode.integer, rm.mode.double,
              rm.mode.complex, rm.mode.raw, rm.mode.character,
              rm.mode.list, rm.mode.expression, rm.mode.name,
              rm.mode.symbol, rm.mode.function)
        )
        print(union(setdiff(ls(envir = .GlobalEnv), save.formula), rm.formula))
        ANSWER <- readline(
            "Are you a sure you want to remove these objects? [yes/no]"
        )
        if (substr(ANSWER, 1, 1) == "n") {
            cat("OK, change your patterns and objects")
        } else {
            rm(
                list = union(
                    setdiff(ls(envir = .GlobalEnv), save.formula),
                    rm.formula
                ),
                envir = .GlobalEnv,
                inherits = inherits
            )
            message("Done!")
        }
    }
}
a <- 1
b <- "female"
c <- FALSE
d <- 4:10
e <- 5
f <- 6
g <- 7
df1 <- 8
df2 <- 9
dfcol <- 10
dff1 <- 11
dfff3 <- 12
mydata1 <- 13
mymydata <- 14
dataframe1 <- data.frame(
    gender = c("F", "M", "M", "F"),
    score = c(10, 12, 14, 18)
    )
matrix.a <- matrix(1:10, nrow = 2, ncol = 5)
matrix2 <- matrix(1:100, ncol = 2)
x <- c("a", "b", "c", "d")
y <- c("d", "e", "f")
```

```{r eval = TRUE, warning=TRUE, message=TRUE}
ls()
rm_versatile(
    rm.objects = list("x", "y"),
    rm.patterns = list("matrix")
)
ls()
```
Let us solve another practical example. Suppose that you have made many 
data frames (for instance 100 data frames) that share similar string pattern in 
their name *e.g.,* "df". You want to remove these objects (which are of `list`
type), and also all other data frames and matrices. One efficient way to do it 
is:
```{r eval = TRUE, warning=TRUE, message=TRUE}
# make lots of data.frames and objects
id <- c(1,2,3,4)
gender <- c("male","female","female","male")
time <- c(2018,2019,2018,2017)
df <- data.frame(id, gender, time)
myvalues <- c(2017,2018,2019)
for (i in 1:100) {
    assign(paste0("dfy",i), df[df$time == myvalues[i],])
}
a <- 1
b <- "female"
c <- FALSE
d <- 4:10
e <- 5
f <- 6
g <- 7
df1 <- 8
df2 <- 9
dfcol <- 10
dff1 <- 11
dfff3 <- 12
mydata1 <- 13
mymydata <- 14
dataframe1 <- data.frame(
    gender = c("F", "M", "M", "F"),
    score = c(10, 12, 14, 18)
    )
matrix.a <- matrix(1:10, nrow = 2, ncol = 5)
matrix2 <- matrix(1:100, ncol = 2)
x <- c("a", "b", "c", "d")
y <- c("d", "e", "f")
# list the objects first
ls()
# let us remove the data frames
rm_versatile(
    rm.patterns = list("df", "matrix", "dataframe"),
    modes = list("list")
)
# check the remaining objects
ls()
```
\* Note that the type of `matrix` objects is not `list`. Matrices are stored as `integer`, hence are not removed from the environment. But we do not want to change the `modes` argument because there are various integer type vectors in 
our environment that are needed. One way to get rid of them is:
```{r echo=FALSE, warning=FALSE, message=FALSE, include = FALSE}
id <- c(1,2,3,4)
gender <- c("male","female","female","male")
time <- c(2018,2019,2018,2017)
df <- data.frame(id, gender, time)
myvalues <- c(2017,2018,2019)
for (i in 1:100) {
    assign(paste0("dfy",i), df[df$time == myvalues[i],])
}
a <- 1
b <- "female"
c <- FALSE
d <- 4:10
e <- 5
f <- 6
g <- 7
df1 <- 8
df2 <- 9
dfcol <- 10
dff1 <- 11
dfff3 <- 12
mydata1 <- 13
mymydata <- 14
dataframe1 <- data.frame(
    gender = c("F", "M", "M", "F"),
    score = c(10, 12, 14, 18)
    )
matrix.a <- matrix(1:10, nrow = 2, ncol = 5)
matrix2 <- matrix(1:100, ncol = 2)
x <- c("a", "b", "c", "d")
y <- c("d", "e", "f")
```
```{r eval = TRUE, warning=TRUE, message=TRUE}
rm_versatile(
    rm.objects = list("matrix.a", "matrix2"),
    rm.patterns = list("df", "matrix", "dataframe"),
    modes = list("list")
)
# check the remaining objects
ls()
```

